Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-13 cosmic_voids.tex
revisada seccion FA profile

In Figure \ref{fig:RhoVel} we show the density and velocity profiles
of voids splitted in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids.

@@

Finally, we also calculate FA profiles in right panels of Fig. \ref{fig:RhoVel}.
A very interesting result from this is a very clear distinction between
the internal profile, below the effective radius, and the external profile. 
For subcompensated voids, they reach quickly the background 
value after $1\reff$. On the other hand, overcompensated voids reach a FA 
ridge at the same radius and then the background value. Central values are
in agreement with those of the density and velocity fields, where larger 
voids exhibit more isotropic cores, associated to higher outflows rates 
and low mass concentrations.

The difference between the radius where the density ridge is reached 
($r\sim 2-4\hMpc$ depending on the void size), and the radius of the FA 
ridge ($r\sim 1-1.5\hMpc$ for all voids) reinforces our previous 
conclusions: before reaching high-density structures like filaments and 
cluster, high-anisotropic, middle-density walls are reached, so the FA 
ridge should be chosen as the natural frontier of voids instead of the
density ridge. This choosing would produce smaller voids as compared with
other voids finding methods, however contamination from external structures
is also avoided.

>>>>

In Figure \ref{fig:density_profile} we show the density and velocity profiles
of voids splitted in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids.

@@

Figure \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
  eff}>1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
For the V-Web the results are similar, albeit rather slowly with the
effective radius.
Overcompensated voids reach a maximum FA at the same effective radiuus
$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

The central FA values also show a magnified trend with the void size. 
Larger voids have lower FA values, more clearly than the same trend
observed with the central density value. 
The voids in the V-Web scheme span a larger range of central FA values
than in the T-Web scheme.

The difference between the radius where the density ridge is reached 
($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
justifies in a more quantiative way the qualitative argument
we present in Section \ref{sec:watershed} to define void boundaries in
our method.  Namely that as we increase the void boundary, we reach
first middle density walls, before reashing high density structures
associated with high anisotropy, making the FA  ridge a  natural voids
boundary instead of the density ridge.

We recognize that our choice produces smaller voids as compared with
other voids finding methods, however this has the advantange of
voiding the contamination from external structures.
